% Here I will describe datasets I am working with 

% Small Graph datasets 

% Big graph datasets 

% What are the challenges and typeical problems 
% with various forms of different datasets 

% OGB dataset 
The OGB dataset is a benchmark dataset.

Benchmark datasets are compiled for developing machine
vision algorithms, and testing and comparing the performance
of different algorithms to identify the most effective solution
to a given biomedical image analysis problem.


In machine learning, benchmarking is the practice of comparing tools
to identify the best-performing technologies in the industry. However,
comparing different machine learning platforms can be a difficult task due
to the large number of factors involved in the performance of a tool.




The Open Graph Benchmark launched in 2019 is perhaps the first attempt
toward this goal trying to introduce challenging graph learning tasks on
interesting real-world graph-structured datasets. One of the hurdles is that
tech companies producing diverse and rich graphs from their users’ activity
are reluctant to share these data due to concerns over privacy laws such as GDPR.
A notable exception is Twitter that made a dataset of 160 million tweets with
corresponding user engagement graphs available to the research community under
certain privacy-preserving restrictions as part of the RecSys Challenge. I hope
that many companies will follow suit in the future.

https://towardsdatascience.com/deep-learning-on-graphs-successes-challenges-and-next-steps-7d9ec220ba8
